paper_replication

### 2021-12-15 paper_replication.Rmd
Update paper_replication.Rmd

EXTENSION:
TODO: use all counties we have data on instead of just those 18 states
TODO: rescore the high vs. low restriction variable to make it make more sense
TODO: add in rural vs urban, % college grad, more variables do a quick variable selection
TODO: repeat for mortality and fertility <- Jo look for this data

>>>>

EXTENSION:
TODO: write literature review and describe motivation for extension
TODO: figure out what is happening with the propensity scores for the extension analyses
TODO: decide whether to rescore the high vs. low restriction variable as a factor or an integer (currently coded as the latter)
TODO: add in rural vs urban and more variables do a quick variable selection
